Concurrent Programming with CXL

### 2020-07-03 book/paper.tex
Latest

\documentclass{report}
\usepackage{fullpage}
\usepackage{imakeidx}\makeindex
\usepackage{hyperref}
\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage[toc]{glossaries}\makeglossaries
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage{bold-extra}

@@

\newcommand{\cxllink}[1]{
    [\href{https://www.cs.cornell.edu/home/rvr/cxl/code/#1}{#1}]
}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1.png}
\caption{The
\href{https://www.cs.cornell.edu/home/rvr/cxl/output/Up.html}{HTML output of running CXL on Figure~\ref{fig:inc}}.
There are three sections.
The top shows the steps to the problematic state.
The bottom left shows the source code and bytecode
of the program.
The bottom right shows the state of each process after the selected step.
Each row in the stack trace of a process shows the current program counter,
the method that is being evaluated, and the line of code that is
being evaluated.}
\label{fig:inchtml1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveLock.png}
\caption{The \href{https://www.cs.cornell.edu/home/rvr/cxl/output/naiveLock.html}{HTML output of running CXL on Figure~\ref{fig:uplock}}.}
\label{fig:naiveLockhtml}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveFlags.png}
\caption{The \href{https://www.cs.cornell.edu/home/rvr/cxl/output/naiveFlags.html}{HTML output of running CXL on Figure~\ref{fig:upflags}}.}
\label{fig:naiveflagshtml}
\end{figure}

>>>>

\documentclass{report}
\usepackage{fullpage}
\usepackage{imakeidx}\makeindex
\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage[toc]{glossaries}\makeglossaries
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage{bold-extra}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{linkbordercolor=blue, pdfborderstyle={/S/U/W 1}}

@@

\newcommand{\cxllink}[1]{
    [\href[pdfnewwindow=true]{https://www.cs.cornell.edu/home/rvr/cxl/code/#1}{#1}]
}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1.png}
\caption{The
\href[pdfnewwindow=true]{https://www.cs.cornell.edu/home/rvr/cxl/output/Up.html}{HTML output of running CXL on Figure~\ref{fig:inc}}.
There are three sections.
The top shows the steps to the problematic state.
The bottom left shows the source code and bytecode
of the program.
The bottom right shows the state of each process after the selected step.
Each row in the stack trace of a process shows the current program counter,
the method that is being evaluated, and the line of code that is
being evaluated.}
\label{fig:inchtml1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveLock.png}
\caption{The \href[pdfnewwindow=true]{https://www.cs.cornell.edu/home/rvr/cxl/output/naiveLock.html}{HTML output of running CXL on Figure~\ref{fig:uplock}}.}
\label{fig:naiveLockhtml}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveFlags.png}
\caption{The \href[pdfnewwindow=true]{https://www.cs.cornell.edu/home/rvr/cxl/output/naiveFlags.html}{HTML output of running CXL on Figure~\ref{fig:upflags}}.}
\label{fig:naiveflagshtml}
\end{figure}
